|

### 2021-10-06 article/article.Rmd
remove citation

Regardless of eventual differences in electoral rules, social composition, and internal procedures, all legislatures share one feature: they are collective bodies. As such, the number of representatives in parliament has important consequences for whole polity. Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{allenrepresentation, crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, Weingastetal1981}. However, how legislature size impacts social welfare remain less understood. On the one hand, enlarged legislatures may increase government spending and lawmaking, which can lead to more public goods \citep{Weingastetal1981}. On the other hand, adding a legislator may increase the number of veto players and exacerbate collective action problems, thus hindering service provision \citep{gottlieb2019countervailing, tsebelis2002veto}. Therefore, what is the effect of larger legislatures on public service provision?

>>>>

Regardless of eventual differences in electoral rules, social composition, and internal procedures, all legislatures share one feature: they are collective bodies. As such, the number of representatives in parliament has important consequences for whole polity. Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, Weingastetal1981}. However, how legislature size impacts social welfare remain less understood. On the one hand, enlarged legislatures may increase government spending and lawmaking, which can lead to more public goods \citep{Weingastetal1981}. On the other hand, adding a legislator may increase the number of veto players and exacerbate collective action problems, thus hindering service provision \citep{gottlieb2019countervailing, tsebelis2002veto}. Therefore, what is the effect of larger legislatures on public service provision?
